Make manuscript figures

### 2021-10-28 scripts/R/make_manuscript_figures.rmd
add standardized poumm param estimates figure

Load data
```{r}
accuracy_simulation_results <- read.delim("output/2021-08-31_estimator_accuracy_MLE.txt")
tpr_simulation_results <- read.delim("output/2021-08-31_GWAS_TPR_MLE.txt")
tree <- ape::read.tree(file = paste(OUTDIR, "pathogen_no_outgroup.newick", sep = "/"))
traits <- read.csv(file = paste(OUTDIR, "poumm_corrected_traits.csv", sep = "/"))
tree <- treeio::full_join(tree, traits, by = "label")
```

@@

POUMM parameter estimates
```{r}

>>>>

Load data
```{r}
accuracy_simulation_results <- read.delim("output/2021-08-31_estimator_accuracy_MLE.txt")
tpr_simulation_results <- read.delim("output/2021-08-31_GWAS_TPR_MLE.txt")
tree <- ape::read.tree(file = paste(OUTDIR, "pathogen_no_outgroup.newick", sep = "/"))
traits <- read.csv(file = paste(OUTDIR, "poumm_corrected_traits.csv", sep = "/"))
tree <- treeio::full_join(tree, traits, by = "label")
POUMM_fit <- get(load(file = paste(OUTDIR, "POUMM_fit.RData", sep = "/")))
```

@@

POUMM parameter estimates
```{r}
# Generate figures, write out estimates
plots <- plot(POUMM_fit, doZoomIn = TRUE, doPlot = F)
p <- plots$densplot +
        scale_fill_manual(
                values = RColorBrewer::brewer.pal(n = 3, name = diverging_palette),
                aesthetics = c("fill", "color"),
                labels = c("Prior", "Chain 1", "Chain 2"),
                name = element_blank()) +
        theme_bw() +
        labs(x = "Value", y = "Density") +
        scale_y_continuous(expand = c(0, 0)) +
        theme(legend.position = "bottom")
ggsave(plot = p, filename = paste(FIGDIR, "poumm_parameter_estimates.png", sep = "/"),
       width = linewidth, height = height, units = "cm")
```
